Sampbias, a method to evaluate geographic sampling bias in species distribution data

### 2019-12-04 manuscript.rmd
manuscript comments skype

>>>>

get the dsitribution from all grid cells and normalize by the number of all available grid cells, not downsampled to the same number of points ignore the starting at 1/intercept

a possion likelihood where the rate i
two paramters, 
1. speed of decae
2. how high is the bias at distance zero

 $b(x,l) = \exp(-lx)$
 $q * exp(-lambda x) / \int_0^\infty (q * exp(-lambda x))$

Average the bias by Akaike wheights, or likelihood
